Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2021-06-21 response_to_reviewers.Rmd

---
title: "Response To Reviewers Comments"
author: "Dan MacLean"
date: "21/06/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Editor,

Thank you for taking the time to send our manuscript for review. Please find attached a list of revisions in response to the reviewers comments that you provided.

We hope that you will find these satisfactory

Sincerely

Prof. Dan MacLean

## Reviewer 1

    1. 'The language in the manuscript needs close attention. For example, the sentence "Deep learning approaches require positive and negative examples from which to learn - here a list of sequences annotated as an effector or not.'

The manuscript was written by a native English speaker and we believe in general that the text is clear, as the same reviewer points out `the authors explained the concepts very clearly`. We have modified the sentence mentioned to read `Deep learning approaches require positive and negative examples from which to learn. We used a list of sequences annotated as an effector or not`

    2. 'This sentence "The larger and more accurate the list the more sensitivity a model can obtain." requires a citation of other works that explore the change in sensitivity with increasing training examples.

No such citation can be made as no study exists. This is because statement is one of a trivial fact about training set size. It is considered self-evident in the field that the more training examples you have, the better predictions can become. We have rephrased to `It is generally held and expected that he larger and more accurate the list the more sensitivity a model can obtain.`

    3. 'It will be nice to conduct a Wilcoxin's [sic] test to ensure that the difference in performance of the different classifiers are significant.'

We understand the impulse behind the suggestion but believe that this is not appropriate for the data presented. The per data set classifications can only be tested once, as they result in the same output for the same input every time, there is no experimental variability. Furthermore, it does not seem really informative to run hypothesis tests on these data, if the reviewer is suggesting pooling the accuracies we'd be testing the hypotheses that accuracy over all test data sets we used the tools on is equal. If one was significant over all data sets it would seem to suggest that the tool was 'better' overall. Our tool would likely come out better over all the datasets, but such a result would mask the more important results about relative performance across kingdoms and different data sets that could guide a user better. The confusion matrices are the best indicators of relative performance characteristics for a given test data set and we use those. Using a single hypothesis test across all data would leave us open to the justified criticism that we had cherry picked a single summary. This is not our intention, so we suggest not to perform this summary statistic and rely on the more explicit, detailed statistics that we have.

    4. 'It will be good to mention the location of the R package next to the sentence "We have produced an R package that will allow other scientists to easily classify their own sequences of interest."'

We have added the link to the R package homepage at the point the reviewer suggests, in addition to its existing places in the manuscript.

    5.  'Can this software be used to predict if a protein is an effector or not? You mentioned how the data was curated for each of the kingdoms. I wonder how the negative data would be constructed if you were to set it up to simply predict if a protein was an effector or not.'

For the first part, yes, this software can be used to predict if a protein is an effector. Our entire manuscript, including the title, and this reviewer point this out in their opening statement `In this manuscript the authors have explored a novel technique to predict effectors` We believe that this point is covered well enough if the reviewer did in fact notice it.

For the second part, we are not sure how to proceed. This seems to be a thought from the reviewer that we have already covered. The reviewer seems to be wondering how we might set up negative data in the case that we want to predict if a protein was an effector. As we do want to predict whether proteins are effectors, and did need negative data, we set it up as fully described in materials and methods, which the reviewer has noted we did. We do not think anything further needs doing for this point.

## Reviewer 2

    1. 'It is a common and most essential practice to train and test methods using different datasets. Authors used 60%, 20% and 20%  for train,test and validation. Is the selection random? How many times authors repeated it with different combination of train,test and validation tests.'

The selection was random at each model, we have updated the section `Encoding and Subsetting Sequences` to reflect this  now reading `Encoded sequences were split into random taxon specific training, test and validation`. The process over hyperparameter scans was repeated 3000 times, resulting in 3000 models being tested. This is described in section `Model Selection and Training`

    2. 'Did the authors checked the performance of the proposed method against the datasets used in the existing methods?'

Yes, we did. This is described in the dedicated section `Comparison With Other Classification Software` and highlighted as `We also evaluated the deep learning models we have developed on the training and hold-out validation sequences used to train the previous methods.` in the second paragraph. Figure 10 shows the results of this.

     3. 'Including a table that shows the sensitivity, specificity and accuracy of the proposed method and existing methods on test/validation dataset will be needed.'

The data are already described in confusion matrices in Figures 6, 9 and 10 and in Figure 8 along with the F1 score.

## Reviewer 3

    1. 'Did authors have performed 3 fold or 5 fold cross-validation?'

We did perform five fold cross-validation in the model training, we have added `Five-fold cross validation was used in all instances.` to the methods section.

    2. 'Authors have selected multiple hyperparameters for each classifiers, and mentioned that they have further chosen some of the hyperparameters to take multiple values and fixed rest of the hyperparameters for each classifier. What criteria were in mind or how authors have decided that which hyperparameters should be fixed and which not? This should be elaborated in methods section. GRID search - explain that.'

As described in the methods section and section `Model Selection and Training` (paragraph 2 and 3), we selected hyperparameters likely to have a strong effect and for those selected random values within likely useful ranges, running a model for each combination, a so-called random search. We present the range and values that we used in the associated supplemental tables. We are not sure why the reviewer has suggested we need to explain a grid search as it is not something we performed. We performed a random search of the space which we have described.

    3. 'Line 35 on page 4,missing figure number.'

This is corrected.

    4. 'Supplementary tables are not in correct order, please correct them.'

This is corrected.

    5. 'In figure 11, it is not clear  what does left, middle and right panel for each taxon represent. Make it more descriptive in figure caption'

We have updated the caption to read: `Grad-CAM activation profiles of CNN-LSTM models  when run with all datasets showing the region of the sequence the model is most able to use to classify (leftmost panel). The most active part of the sequences are shown in logo plots of sequences extracted from the activation region within the dotted lines for effector data (centre panel) and non-effector data (rightmost panel). A: Models trained on bacterial sequences; B: Models trained on fungal sequences; C: Models trained on oomycete sequences.`

### 2021-06-21 main.Rmd
updates for reviewers

---
title: "Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm_latex.tex
    toc: no
    includes:
      in_header: preamble.tex
fontsize: 12pt
fontfamily: sans
papersize: a4paper
author:
  - name: Ruth Kristianingsih, Dan MacLean
  - affiliation: The Sainsbury Laboratory, University of East Anglia, Norwich Research Park, Norwich, UK, NR4 7JJ, dan.maclean@tsl.ac.uk
abstract: ""
geometry: margin=1in
biblio-style: apsr
bibliography: ["r-references.bib"]
graphics: yes
header-includes:
  - \usepackage{amsmath}
  - \usepackage{siunitx}
  - \usepackage{float}
---

@@

fig_caption("activations", "Grad-CAM activation profiles of CNN-LSTM models  when run with all datasets; and sequence logo plots of sequence in the activation region within the dotted lines for effector data (left panel) and non-effector data (right panel). A: Models trained on bacterial sequences; B: Models trained on fungal sequences; C: Models trained on oomycete sequences.")

@@

Deep learning approaches require positive and negative examples from which to learn - here a list of sequences annotated as an effector or not. The larger and more accurate the list the more sensitivity a model can obtain. It is critical that training examples are experimentally verified effectors. Much of the effector annotation in public genomics databases is from computational predictions of genomics and is therefore of experimentally unverified hypothetical effectors. A good source of experimentally verified data is in the Molecular Plant Microbe Interactions (MPMI) literature and The widest ranging manual curation of MPMI papers is being performed as part of the PHI-Base [@phibase] database strategy, PHI-base is an expertly curated database of genes proven experimentally to affect the outcome of pathogen host interactions and is therefore an excellent source of reliable effector sequences.

Here we use combinations of CNNs that do not rely on _a priori_ feature selection to classify experimentally verified effectors and non-effectors in three taxa of plant pathogen: bacterial, fungal and oomycete. We show that these have very strong predictive power, can outperform existing effector prediction methods in accuracy and a better balance of sensitivity and specificity.  We also analyse the activations of the models in response to effectors and non-effectors to gain insights into the sequence features that are allowing classification. We have produced an R package that will allow other scientists to easily classify their own sequences of interest.

@@

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data prepared on request by the PHI-Base team, the file can be accessed at [https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv](https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv). The pipeline in Figure \@ref(effectorcollection) outlines the steps used. We filtered plant effector proteins and their taxonomic groups and collected sequences from UniProt Release 2019_05, using the code in [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd). We created a correspondingly sized data set of non-effectors with secretion signals originating in species matched to those from which the effectors were drawn. We downloaded sequences for randomly selected proteins matching these criteria from Ensembl databases [@yates2020] : specifically Ensembl Fungi, Protists and Bacteria manually using the BioMart tools [@smedleybiomart2009]. Since the BioMart tool is not available on Ensembl Bacteria, we downloaded whole proteome protein sequnces from species matched to those from which the effector came using FTP. With these we used SignalP 3.0 [@dyrlovbendtsen2004] in order to filter the secreted sequences and selected accordingly. We used default paramaters from SignalP, except the type of organism group which is `euk` for both fungi and oomycete sequences, and `gram-` or `gram+` for bacteria sequences. Redundant sequences were filtered using BLASTp [@camachoblast2009]. We achieved these steps using the code in [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd).

@@

The sequences collected were encoded using either one-hot encoding (CNN-LSTM based models) or integer based encoding (CNN-GRU-LSTM models). Sequences were post-padded with zeroes to bring the vectors to identical lengths to each other and the longest sequence in the taxon data set. The longest sequence  for bacteria, fungi, and oomycete are 2574, 4034, and 934, respectively. Encoded sequences were split into taxon specific training, test and validation sets at a 60%, 20%, 20% split respectively as described in code at [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0008_split_and_encode.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0008_split_and_encode.Rmd)

@@

Hyperparameter scans were performed using random search, a hyperparameter optimization method where each hyperparameter setting is randomly sampled from a distribution of possible hyperparameter values [@Bergstra2012]. We used RandomSearchCV(), the implementation of random search in `scikit-learn 0.19.2` [@scikitlearn] together with KerasClassifier() which is an implementation of the scikit-learn classifier API for keras. Code for this can be found in [https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/hyperparameter-scan-scripts](https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/hyperparameter-scan-scripts). All model training was performed as described in section Model Training.

@@

Fine tuning was performed manually using `keras 2.2.4` together with metrics module and KFold cross validator from `scikit-learn 0.19.2`. Scripts implementing the tuning can be found at  [https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/manual_tune_scripts](https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/manual_tune_scripts).

@@

```{r, bacefftable, echo=FALSE, message = FALSE}
apa_table(
  readr::read_tsv("tables/bacterial_effector_count.tab"),
  digits = 0,
  align = 'c',
  caption = 'Bacterial species contributing to the bacterial effector sequence set retrieved from PHI-Base',
  placement = "h"
)
```

```{r, fungiefftable}
apa_table(
  readr::read_tsv("tables/fungal_effector_count.tab"),
  digits = 0,
  align = 'c',
  caption = 'Fungal species contributing to the fungal effector sequence set retrieved from PHI-Base'
)
```

```{r, oomefftable}
apa_table(
  readr::read_tsv("tables/oomycete_effector_count.tab"),
  digits = 0,
  align = 'c',
  caption = 'Oomycete species contributing to the oomycete effector sequence set retrieved from PHI-Base'
)
```

```{r, possiblecombination}
apa_table(
  readr::read_tsv("tables/possible_combination_each_model.tab"),
  digits = 0,
  align = 'c',
  caption = 'List of possible combination of hyperparamaters setting for each model'
)
```

```{r, fixedhyperparam}
# apa_table(
#   readr::read_tsv("tables/fixed_hyperparam.tab"),
#   digits = 0,
#   align = 'c',
#   caption = 'Hyperparameters fixed in automatic scanning of hyperparameter space for each model'
# )

readr::read_tsv("tables/fixed_hyperparam.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters fixed in automatic scanning of hyperparameter space for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 7)
```

```{r, tunedhyperparam}
# apa_table(
#   readr::read_tsv("tables/tuned_hyperparam.tab"),
#   digits = 0,
#   align = 'c',
#   caption = 'Hyperparameters tuned in manual scanning of hyperparameter space for each model'
# )

readr::read_tsv("tables/tuned_hyperparam.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters tuned in manual scanning of hyperparameter space for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 7)
```

```{r, hyperparam}
readr::read_tsv("tables/hyperparamscan_info.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters used in automatic scanning of hyperparameter space and best performing parameters values for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 7)
```

>>>>

---
title: "Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm_latex.tex
    toc: no
    includes:
      in_header: preamble.tex
fontsize: 12pt
fontfamily: sans
papersize: a4paper
author:
  - name: Ruth Kristianingsih, Dan MacLean
  - affiliation: The Sainsbury Laboratory, University of East Anglia, Norwich Research Park, Norwich, UK, NR4 7UH, dan.maclean@tsl.ac.uk
abstract: ""
geometry: margin=1in
biblio-style: apsr
bibliography: ["r-references.bib"]
graphics: yes
header-includes:
  - \usepackage{amsmath}
  - \usepackage{siunitx}
  - \usepackage{float}
  - \usepackage{placeins}
---

@@

fig_caption("activations", "Grad-CAM activation profiles of CNN-LSTM models  when run with all datasets showing the region of the sequence the model is most able to use to classify (leftmost panel). The most active part of the sequences are shown in logo plots of sequences extracted from the activation region within the dotted lines for effector data (centre panel) and non-effector data (rightmost panel). A: Models trained on bacterial sequences; B: Models trained on fungal sequences; C: Models trained on oomycete sequences.")

@@

Deep learning approaches require positive and negative examples from which to learn. We used a list of sequences annotated as an effector or not. It is generally held and expected that he larger and more accurate the list the more sensitivity a model can obtain. It is critical that training examples are experimentally verified effectors. Much of the effector annotation in public genomics databases is from computational predictions of genomics and is therefore of experimentally unverified hypothetical effectors. A good source of experimentally verified data is in the Molecular Plant Microbe Interactions (MPMI) literature and The widest ranging manual curation of MPMI papers is being performed as part of the PHI-Base [@phibase] database strategy, PHI-base is an expertly curated database of genes proven experimentally to affect the outcome of pathogen host interactions and is therefore an excellent source of reliable effector sequences.

Here we use combinations of CNNs that do not rely on _a priori_ feature selection to classify experimentally verified effectors and non-effectors in three taxa of plant pathogen: bacterial, fungal and oomycete. We show that these have very strong predictive power, can outperform existing effector prediction methods in accuracy and a better balance of sensitivity and specificity.  We also analyse the activations of the models in response to effectors and non-effectors to gain insights into the sequence features that are allowing classification. We have produced an R package that will allow other scientists to easily classify their own sequences of interest, available at [https://ruthkr.github.io/deepredeff](https://ruthkr.github.io/deepredeff).

@@

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data prepared on request by the PHI-Base team, the file can be accessed at [https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv](https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv). The pipeline in `r fig_caption("effectorcollection", display="cite")` outlines the steps used. We filtered plant effector proteins and their taxonomic groups and collected sequences from UniProt Release 2019_05, using the code in [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd). We created a correspondingly sized data set of non-effectors with secretion signals originating in species matched to those from which the effectors were drawn. We downloaded sequences for randomly selected proteins matching these criteria from Ensembl databases [@yates2020] : specifically Ensembl Fungi, Protists and Bacteria manually using the BioMart tools [@smedleybiomart2009]. Since the BioMart tool is not available on Ensembl Bacteria, we downloaded whole proteome protein sequnces from species matched to those from which the effector came using FTP. With these we used SignalP 3.0 [@dyrlovbendtsen2004] in order to filter the secreted sequences and selected accordingly. We used default paramaters from SignalP, except the type of organism group which is `euk` for both fungi and oomycete sequences, and `gram-` or `gram+` for bacteria sequences. Redundant sequences were filtered using BLASTp [@camachoblast2009]. We achieved these steps using the code in [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd).

@@

The sequences collected were encoded using either one-hot encoding (CNN-LSTM based models) or integer based encoding (CNN-GRU-LSTM models). Sequences were post-padded with zeroes to bring the vectors to identical lengths to each other and the longest sequence in the taxon data set. The longest sequence  for bacteria, fungi, and oomycete are 2574, 4034, and 934, respectively. Encoded sequences were split into random taxon specific training, test and validation sets at a 60%, 20%, 20% split respectively as described in code at [https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0008_split_and_encode.Rmd](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0008_split_and_encode.Rmd).

@@

Hyperparameter scans were performed using random search, a hyperparameter optimization method where each hyperparameter setting is randomly sampled from a distribution of possible hyperparameter values [@Bergstra2012]. Hyperparameters to vary were selected as the ones generally known and expected to have strongest effect. We used RandomSearchCV(), the implementation of random search in `scikit-learn 0.19.2` [@scikitlearn] together with KerasClassifier() which is an implementation of the scikit-learn classifier API for keras. Code for this can be found in [https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/hyperparameter-scan-scripts](https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/hyperparameter-scan-scripts). All model training was performed as described in section Model Training.

@@

Fine tuning was performed manually using `keras 2.2.4` together with metrics module and KFold cross validator from `scikit-learn 0.19.2`. Scripts implementing the tuning can be found at  [https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/manual_tune_scripts](https://github.com/TeamMacLean/ruth-effectors-prediction/tree/master/scripts/python-scripts/manual_tune_scripts). Five-fold cross validation was used in all instances.

@@

```{r, bacefftable, echo=FALSE, message = FALSE}
  readr::read_tsv("tables/bacterial_effector_count.tab") %>% 
  knitr::kable( "latex",
  digits = 0,
  align = 'c',
  caption = 'Bacterial species contributing to the bacterial effector sequence set retrieved from PHI-Base'
) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header","hold_position"), font_size = 7)
```

```{r, fungiefftable}
  readr::read_tsv("tables/fungal_effector_count.tab") %>% 
  knitr::kable( "latex",
  digits = 0,
  align = 'c',
  caption = 'Fungal species contributing to the fungal effector sequence set retrieved from PHI-Base'
) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header","hold_position"), font_size = 7)
```

```{r, oomefftable}
  readr::read_tsv("tables/oomycete_effector_count.tab") %>% 
  knitr::kable( "latex",
  digits = 0,
  align = 'c',
  caption = 'Oomycete species contributing to the oomycete effector sequence set retrieved from PHI-Base'
) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header","hold_position"), font_size = 7)
```

```{r, possiblecombination}

  readr::read_tsv("tables/possible_combination_each_model.tab")%>% 
  knitr::kable( "latex",
  digits = 0,
  align = 'c',
  caption = 'List of possible combination of hyperparamaters setting for each model'
) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header","hold_position"), font_size = 7)
```
\newpage
```{r, fixedhyperparam}
# apa_table(
#   readr::read_tsv("tables/fixed_hyperparam.tab"),
#   digits = 0,
#   align = 'c',
#   caption = 'Hyperparameters fixed in automatic scanning of hyperparameter space for each model'
# )

readr::read_tsv("tables/fixed_hyperparam.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters fixed in automatic scanning of hyperparameter space for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header","hold_position"), font_size = 7)
```
\newpage
```{r, tunedhyperparam}
# apa_table(
#   readr::read_tsv("tables/tuned_hyperparam.tab"),
#   digits = 0,
#   align = 'c',
#   caption = 'Hyperparameters tuned in manual scanning of hyperparameter space for each model'
# )

readr::read_tsv("tables/tuned_hyperparam.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters tuned in manual scanning of hyperparameter space for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header", "hold_position"), font_size = 7)
```

```{r, hyperparam}
readr::read_tsv("tables/hyperparamscan_info.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters used in automatic scanning of hyperparameter space and best performing parameters values for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header", "hold_position"), font_size = 7)
```
